Supplementary Material \\ \large{Heterogenous firing responses leads to diverse coupling to presynaptic activity in mice layer V pyramidal neurons}

### 2016-08-04 derivation_supplementary/supplementary.tex
adding larkum et al. morphology and mechanisms

% Created 2016-06-19 Sun 00:51
\documentclass[colorlinks]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}
%% \tolerance=1000
\hypersetup{allcolors = blue} % to have all the hyperlinks in 1 color
\renewcommand{\refname}{\vspace{-.8cm}}
\usepackage{jneurosci}
\bibliographystyle{jneurosci}
\author{Y. Zerlaut \& A. Destexhe}
\date{\today}
\title{Supplementary Material \\ \large{Heterogenous firing responses leads to diverse coupling to presynaptic activity in a simplified morphological model of layer V pyramidal neurons}}
\begin{document}

>>>>

% Created 2016-06-19 Sun 00:51
\documentclass[colorlinks]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}
%% \tolerance=1000
\hypersetup{allcolors = blue} % to have all the hyperlinks in 1 color
\renewcommand{\refname}{\vspace{-.8cm}}
\usepackage{jneurosci}
\bibliographystyle{jneurosci}
\author{Y. Zerlaut \& A. Destexhe}
\date{\today}
\title{Supplementary Material \\ \large{Heterogenous firing responses leads to diverse coupling to presynaptic activity in mice layer V pyramidal neurons}}
\begin{document}
